Relationships in the extremes and their influence on competition and coexistence

### 2021-07-08 paper/Paper.Rnw
more intro work

While there are multiple studies on the influence of extremes (due to climate change), the influence of relationships in their extremes (also due to climate change), has not yet been explored. The lottery model within the framework of coexistence theory provides a suitable opportunity to explore extreme relationships and the consequences to coexistence.

>>>>

[As we know], anthropogenic climate change has large consequences for almost all aspects of life. Extreme climatic events have only become more extreme - increasing in magnitude and frequency - as climate change has progressed and have contributed to an increase in global means as well an an increase in environmental variability. While there are multiple studies on the influence of environmental extremes and varaibility (Parepa et al 2013, Diez et al 2012), the influence of relationships and interactions between drivers in their extremes, has not yet been explored. Encapsulated by ATAs Tail associations are relationships in the extremes .  Environmental variability has been classically shown to promote coexistence via storage mechanisms (Chesson & Warner 1981, Warner & Chesson 1985), thus we continue/move forward with this simple model to examine extreme relationships between environmental variables on the contribution of storage effects to coexistence.

The lottery model within the framework of coexistence theory provides a suitable opportunity to explore extreme relationships and the consequences to coexistence.
